\cvsection{Projects}
\begin{cventries}
	\cventry
		{Trapped Ion Quantum Information Group, Department of Physics ETHZ}
		{Development of an RF resonator for a double junction ion trap}
		{Zurich, Switzerland}
		{Sep. 2018 -- Mar. 2019}
		{
			\begin{cvitems}
				\item {Calculated optimal parameters for a helical resonator filtering and amplifying RF signal for an ion trap}
				\item {Designed tunable helical resonator for the cryogenic setup in Autodesk Inventor}
				\item {Produced device complying with engineering limitations}
				\item {Compared experimental output with modeled predictions}
			\end{cvitems}
		}

	\cventry
		{Laboratory of Nanophotonics \& Metamaterials, Quantum Electronics Department, Faculty of Physics MSU}
		{Nonlinear nanophotonics based on Mie-resonant semiconductor nanostructures}
		{Moscow, Russia}
		{Sep. 2015 -- Jun. 2016}
		{
			\begin{cvitems}
				\item {Calculations of optimal geometric parameters of silicon waveguides, nanodisks or their ordered arrays, optically bounded with waveguides and nanodisk chains }
				\item {Fabrication of optically bounded silicon nanostructure samples}
				\item {Investigation of linear spectrums and transmittance of waveguides in wide spectral range, overlapping nanodisk Mie-resonant frequencies }
				\item {Investigation of nonlinear optical response and all-optical switching phenomena in created nanostructures via methods of microscopy of optical harmonics generation, four-wave mixing and ``pump''-``probe'' technique}
			\end{cvitems}
		}

	\cventry
		{Summer internship at Department of Physics, Faculty of Science, Tohoku University}
		{Evaluation of effective permittivity and permeability of artificial structures}
		{Tohoku, Japan}
		{Jul. 2015 -- Aug. 2015}
		{
			\begin{cvitems}
				\item {Used an electromagnetic simulator (CST Microwave Studio) to design the structures}
				\item {Fabricated own structures by photolithography technique}
				\item {Characterized the sample using conventional spectrometer and Atomic Force Microscope}
				\item {Measured phase information with Mach-Zehnder interferometer}
				\item {Retrieved effective permittivity and permeability based on an algorithm (MATLAB \& Wolfram Mathematica)}
			\end{cvitems}
		}
	
	\cventry
		{
			Quantum Information Laboratory, Department of Quantum Electronics, Faculty of Physics MSU
		}
		{
			Relativistic quantum cryptography and cryptography based on PTC (Phase Time Coding)
		}
		{Moscow, Russia}
		{Dec. 2013 - Jun. 2014}
		{
			\begin{cvitems}
				\item {Investigated various interferometric schemes capable of revealing non-classical features of biphoton field generated in the process of SPDC}
				\item {Got basic understanding of quantum cryptography protocols and atacs on them}
			\end{cvitems}
		}
		
\end{cventries}
